A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-04-13 graph_syntax.tex
fixing stuff from change to sellar

\subsection{In-degree and Out-degree}
	\label{s:indegree-outdegree}
	The \emph{in--degree} of a node is the number of connection edges directed in and 
	is denoted as $\txt{deg}^-(v)$, and the \emph{out--degree} 
	is the number of connection edges directed out and it is denoted as $\txt{deg}^+(v)$.
	The degree of a given node is only a function of the connection edges 
	attached to it. The number of implicit edges is not relevant since any number 
	of drivers could be involved, at different parts of an solution process. For 
	example in a sequential optimization where a global optimizer is first applied
	and a gradient based one is applied second, design variables would have incomming 
	implicit edges from both optimizers but this would not affect the in--degree of those
	variable nodes. 
	((DP:I started to remove any reference to the edge type in these definitions but then saw that you needed it. The reason I did that was because in--degree and out--degree are basic graph theory terms. What if the reference to implicit edges is handled with the upper in--degree limit, i.e. after the FPG is obtained the upper indegree limit for the design variable nodes is relaxed (increased) so that it isn't a problem what is or isn't counted?))

	((DP:the definitions were in/out degree were not in my book, I had to get them from wikipedia, where they are spelled indegree and outdegree))

	We also define the \emph{upper in--degree limit}

	\begin{equation}
	\txt{deg}_u^-(v):V \to \mathbb{N}
	\end{equation} 
	and the \emph{lower in--degree limit} as
	\begin{equation}
	\txt{deg}_l^-(v):V \to \mathbb{N}.
	\end{equation}
	These user-specified limits govern the number of connection edges that may be directed into a variable
	node for a valid graph. Consider a variable node $v$ with
	$\txt{deg}_u^-(v) = \txt{deg}_l^-(v) = 1$. In this case, $v$ must have exactly one
	incomming explicit edge or the graph is invalid. Two possiblities exist for voilating 
	these limit conditions: 
	\begin{description}
	  \item[hole: ] The number of incomming edges is less than the lower indegree limit:
		\begin{equation} \txt{deg}^-(v) < \txt{deg}_l^-(v) \label{e:hole} \end{equation}
		This represents a lack of information being supplied to the node.

  \item[collision: ] The number of incomming edges is greater than $ \txt{deg}_u^-(v)$. 
    \begin{equation} \txt{deg}^-(v) > \txt{deg}_u^-(v) \end{equation}
\end{description} 
These violations will be managed in order to seek a working problem formulation.

@@

%As discussed in Sec.((intro)), the digraph must be able to describe the individual aspects of an MDAO problem.
\subsection{Analysis Blocks and Connections}
\label{ss:analysis blocks and connections}
Analysis tools take in a number input variables and then perform some work to calculate 
the values for their respective outputs. In an MDAO graph, this process is 
represented by a group of nodes and edges called an \emph{analysis block}, 
shown in Fig. \ref{f:analysis block}. Within an analysis block each variable 
node represents a single input or output and is connected 
to a single model node via a fixed edge. Note that in Fig. \ref{f:analysis block}, 
the analysis block contains two model nodes, with a single edge connecting them. 
This edge represents the necessary calculations to map given inputs 
to proper output values. If constructing a weighted graph, the weight calculation edge 
provides the opportunity to computational cost. However, it is also allowed to skip 
this edge and have both incomming and outgoing edges to variables through a single model 
node for a given analysis block. Although analysis blocks are comprised of multiple nodes and edges, since all 
the edges within them are fixed, they become fixed sub-graphs within a graph.

@@

	Variable nodes in an analysis block can be distinguished as either an input or an output by the manner in which they are connected. As shown in Fig.~\ref{f:analysis block}, inputs are any variable nodes that have an outgoing edge into a model 
	node. Conversely, outputs are any variable nodes that have an incoming edge from a model node. 
	Note that by this definition, inputs and outputs can only exist when variable nodes poses an 
	edge joining them to a model node. 
	((DP:I'm not sure what the sentences before or after this comment mean))
	These are labeled out as 
	local inputs and local outputs. The variables are local because they are explicitely tied
	to the analysis block and have no relevance without it.

@@

So a design variable is defined as any variable node with $\txt{deg}_l^-(v)=0$. 
This, by definition, means that design variables are not holes in the graph, since 
they have not violated their lower in-degree limit. Regardless, 
when working with a MCG or FPG, only connection edges are allowed, so a design 
variable in either graph will be a variable with no incomming edges edges. For a valid PSG 
any design variable node would have at least one, but possibly multiple, incomming 
implicit edges from one or more driver nodes.

@@

  Simply stating that any node or block with incomming or outgoing edges
  from more than one other node or block is global works glosses over a more 
  subtle aspect of some MDAO problems. The locality of any node in a graph is 
  a relative property. For instance, a single node might have outgoing edges 
  to two separate analysis blocks, $A$ and $B$, but none to a third, $C$. Then 
  you could say that this node was global with respect to $A$ and $B$, but local 
  to the group $A,B$ with respect to $C$. This situation produces a natural 
  hierarchy in a graph, where you can form increasingly smaller groups as you 
  segment problem into finer localities. When solving a problem using 
  a heirarchical decomposition approach, there are various techniques for 
  partitioning that are effective in different scenarios 
  \cite{krishnamachari1997optimal,Perez2004,sobieszczanski1997,allison2009optimal,michelena1997hypergraph}.

@@

  Coupling exists in a design problem when a set of two or more analyses each depend on the
  others outputs. Consider the notional problem from section \ref{sec:spg_vs_fpg} where two 
  analyses, $A$ and $B$ are coupled through their respective variables. The graph of this 
  is shown in Fig. \ref{f:coupling}. In the graph $A.z$ has an outgoing connection 
  edge to $B.z$, indicating that there is a connection between the two. 
  Similarly a connection exists between $B.y$ and $A.y$. These two connections form 
  a cycle which represent the coupling between them. This cycle means that blocks $A$ and $B$ need
  to be iterated on untill they converge.

@@

	It is important to note that the cycle in graph in Fig.~\ref{f:coupling} does not contain 
	any driver nodes. That means that no solver, optimizer, or other iterative construct is 
	invovled in the coupling. This absence is intentional, as the coupling is an inherent part 
	of the problem. This corresponds directly to Eqn.~\ref{eqn:simple_fpf}, where 
	each equality constraint is one edge in the graph. Transitioning to either 
	Eqn.~\ref{eqn:simple} or Eqn.~\ref{eqn:simple2} means selecting one of the nodes as the starting point 
	for the iteration and indicating which associated analysis block should be executed first.

	Larger problems can contain more complex cycles in their FPG, indicating more 
	complex coupling between analyses. A cycle can contain more than 
	just two analysis blocks. Multiple independent cycles can exist, indicating 
	independent coupling relationships. Cycles can also overlap, where the same analysis 
	blocks are involved in multiple different coupling cycles. All of these situations
	arise naturally as the size of problems grows, and managing this coupling may
	become difficult. From the perspective of the graph, the problem reduces down to 
	an ordering challenge. For each cycle in the graph, an analysis block needs to be selected 
	to start the iteration from. Rogers' DEMAID tool uses a genetic algorithm to find an ordering 
	that minimizes the overall coupling of the system by separating independent 
	cycles in the graph \cite{rogers1996,rogers1996demaid}. In the present work, Sec.~\ref{s:example problem}.\ref{ss:obtaining an FPG} will suggest that an FPG may be obtained with respect to the number of cycles or the length of these cycles, etc.

\subsection{Multi--fidelity Problems}
	\label{ss:multi-fideliy problems}
	A multi--fidelity problem can be characterized by two or more different analyses 
	each calculating the same data. Mapping this type of multi--fidelity situation 
	onto a graph will yield two analysis blocks, each with their own output 
	variable nodes, having outgoing edges to a third analysis block that needs the 
	data as input. Figure \ref{f:collision-example} shows a notional problem 
	that exhibits this structure, where the key feature is that variable node $y$ in 
	analysis block $C$ has two incoming edges. 
	\begin{figure}
	  \begin{center}
	  %\includegraphics[height=.25\textheight]{}
	  [INSERT GRAPH HERE]
	  \caption{Graph of a notional multi-fidelity problem \label{f:collision-example}}
	  \end{center}
	\end{figure}

@@

\subsection{Fundamental Problem Graph}
	\label{ss:FPG}
	We now define the fundamental problem graph $F=(V_F,E_F)$ as a directed graph meeting the following conditions, which are explained subsequently,
	\begin{enumerate}
	\item[(1)] $\displaystyle{I_F \subset I}$ such that the remaining conditions hold
	\item[(2)] $\displaystyle{ \forall i \in I_F, \ \exists v \in V_{A_i} \txt{ with } t_\txt{node}(E^{-1}(v))=\txt{`model'} \txt{ and } \txt{deg}^+(v)>0 }$
	%\item[(3)] $\displaystyle{ \forall i \in I, \forall v \in V_{A_i} \txt{ with } t_\txt{node}(v) = \txt{`variable,'} \  \txt{deg}_l^-(v) < \txt{deg}^-(v) \leq \txt{deg}_u^-(v)}$
	%\item[(3)] $\displaystyle{ \forall i \in I, \forall v \in V_\txt{out} \txt{ with } t_\txt{node}(v) = \txt{`variable,'} \  \txt{deg}_l^-(v) < \txt{deg}^-(v) \leq \txt{deg}_u^-(v)}$
	\item[(3)] $\displaystyle{V_{\txt{in},F} = \{v \in V_\txt{in} \st \txt{deg}^+(v) > 0\} }$ ((maybe this should be 1 instead of 0 to match the previous definition of global input))
	\item[(4)] $\displaystyle{V_F = V_{\txt{in},F} \cup V_\txt{out} \cup \left( \bigcup_{i \in I_F} V_{A_i} \right)}$
	\item[(5)] $\displaystyle{E_F = C_F \cup \left( \bigcup_{i \in I_F} E_{A_i} \right), \ C_F \subset C_M}$
	\item[(6)] $\displaystyle{\forall v \in V_F \txt{ with } t_\txt{node}(v) = \txt{`variable,'} \  \txt{deg}_l^-(v) \leq \txt{deg}^-(v) \leq \txt{deg}_u^-(v)}$
	\end{enumerate}
	The set $I_F$ is an index set containing the indices of the analysis blocks in $F$ and it may only include the analysis blocks $A_i$ that meet requirements (2) and (6). 
	Requirement (2) stipulates that each analysis blocks in $F$ must have at least one local output that is being used. 
	Requirement (3) stipulates that only the global inputs that are being used should be included. 
	Requirements (4) and (5) provide the construction of the sets of nodes and edges, respectively. 
	Lastly, requirement (6) stipulates that the number of edges directed into the variable nodes must be within the lower and upper in-degree limits; if $\txt{deg}^-(v) < \txt{deg}_l^-(v)$ the node is called a \emph{hole}, and if $\txt{deg}^-(v) > \txt{deg}_u^-(v)$ the node is called a \emph{collision}.

@@

	%Then, mathematically, the FPG starts with $\mathcal A_1 = \{1,\ldots,m\}$, $I_{F,1} = I$, and $C_{F,1} = C_M$.
	Then, mathematically, the FPG starts with $C_{F,0} = C_M$, $E_{F,0} = E_M$, $V_{F,0} = V_M$.
	The nodes where $\txt{deg}^-(v) < \txt{deg}_l^-(v)$ are considered first.
	\begin{enumerate}
	\item The first step is to detect holes and disconnect the connection edges following them. These connection edges are removed because they represent variables which cannot be determined because the analysis function does not have adequate inputs. The set of variable nodes which are holes is created as
	\begin{equation}
	H = \{v \in V_M \st t_\txt{node}(v) = \txt{`variable'} \txt{ and } \txt{deg}^-(v) < \txt{deg}_l^-(v) \},
	\end{equation}
	which is the set of variable nodes with fewer incoming edges than are allowed by the lower in-degree limit.
	Then the updated set of edges is created by removing the first set of connection edges following the hole:
	\begin{equation}
	C_{F,1} = C_{F,0} \setminus \{(x,y) \in E_M \st x=E_M^3(v) \txt{ for } v \in H\},
	\end{equation}
	%deg-v is now recaculated for the new C. 
	and this step is demonstrated by Fig.~\ref{f:hole}. Because removing these edges can create new holes, this step must be repeated until no more holes are found.
	\begin{figure}[htb!]
		\begin{center}
		\includegraphics[width=3in]{images/analysis_block_hole}
		\end{center}
		\vspace{-20pt}
	\caption{Example variable node indicating a hole.}
	\label{f:hole}
	\end{figure}

	\item The second step is to detect collisions and to then disconnect enough connection edges so that the collisions are resolved. The set of variable nodes which contain collisions is created as
	\begin{equation}
	S_\txt{nodes} = \{v \in V_M \st t_\txt{node}(v) = \txt{`variable'} \txt{ and } \txt{deg}^-(v) > \txt{deg}_u^-(v) \}.
	\end{equation}
	For each collision node we can construct a set contained the edges directed in. The set containing all of these sets is constructed as
	\begin{equation}
	S_\txt{edges} = \big \{ \{(x,y) \in E_M\} \st y \in S_\txt{nodes} \big \}
	\end{equation}
	Let $J=\{1,2,\ldots,|S_\txt{edges}|\}$ be an indexing set for $S_\txt{edges}$ such that each $S_{\txt{edges},j}$ corresponds to a set in $S_\txt{edges}$ for $j \in J$. 
	An example collision is shown in Fig.~\ref{f:collision} to indicate the definition of $S_{\txt{edges},j}$. 
	We can assume that $J$ also indexes $S_\txt{nodes}$ because there is a one--to--one correspondence between the elements in $S_\txt{nodes}$ and the elements in $S_\txt{edges}$ (which are sets). 
	Then we may construct sets of edges as
	\begin{equation}
	B_j = \big \{e_k \in S_{\txt{edges},j} \st k \in \{1,2,\ldots,K\} \txt{ with } K \leq \txt{deg}_u^-(v_j) \big \}, \ j \in J,
	\end{equation}
	which means that each set $B_j$ is constructed from the set $S_{\txt{edges},j}$ by taking only as many edges as are allowed by the upper in--degree limit of $v_j$. The construction of each $B_j$ corresponds to making a decision on which edges to include and which edges not to include. Then let
	\begin{equation}
	C_{F,2} = \{ e \in C_{F,1} \st e \in B_j \txt{ for some } j \in J\},
	\end{equation}
	\begin{equation}
	E_{F,2} = E_M \setminus (C_M \setminus C_{F,2})
	\end{equation}
	and
	\begin{equation}
	F_2 = (V_M,E_{F,2})
	\end{equation}
	\begin{figure}[htb!]
		\begin{center}
		\includegraphics[width=3in]{images/analysis_block_collision}
		\end{center}
		\vspace{-20pt}
	\caption{Example variable node indicating a collision.}
	\label{f:collision}
	\end{figure}

>>>>

\subsection{indegree and outdegree}
	\label{s:indegree-outdegree}
	The \emph{indegree} of a node is the number of connection edges directed in and 
	is denoted as $\txt{deg}^-(v)$, and the \emph{outdegree} 
	is the number of connection edges directed out and it is denoted as $\txt{deg}^+(v)$.
	The degree of a given node is only a function of the connection edges 
	attached to it. The number of implicit edges is not relevant since any number 
	of drivers could be involved, at different parts of an solution process. For 
	example in a sequential optimization where a global optimizer is first applied
	and a gradient based one is applied second, design variables would have incomming 
	implicit edges from both optimizers but this would not affect the indegree of those
	variable nodes. 
	((DP:I started to remove any reference to the edge type in these definitions but then saw that you needed it. The reason I did that was because indegree and outdegree are basic graph theory terms. What if the reference to implicit edges is handled with the upper indegree limit, i.e. after the FPG is obtained the upper indegree limit for the design variable nodes is relaxed (increased) so that it isn't a problem what is or isn't counted?))

	We also define the \emph{upper indegree limit}

	\begin{equation}
	\txt{deg}_u^-(v):V \to \mathbb{N}
	\end{equation} 
	and the \emph{lower indegree limit} as
	\begin{equation}
	\txt{deg}_l^-(v):V \to \mathbb{N}.
	\end{equation}
	These user-specified limits govern the number of connection edges that may be directed into a variable
	node for a valid graph. Consider a variable node $v$ with
	$\txt{deg}_u^-(v) = \txt{deg}_l^-(v) = 1$. In this case, $v$ must have exactly one
	incomming explicit edge or the graph is invalid. Two possiblities exist for voilating 
	these limit conditions: 
	\begin{description}
	  \item[hole: ] The number of incomming edges is less than the lower indegree limit:
		\begin{equation} \txt{deg}^-(v) < \txt{deg}_l^-(v) \label{e:hole} \end{equation}
		This represents a lack of information being supplied to the node.

  \item[collision: ] The number of incomming edges is greater than $ \txt{deg}_u^-(v)$. 
    \begin{equation} \txt{deg}^-(v) > \txt{deg}_u^-(v) \label{e:collision}\end{equation}
\end{description} 
These violations will be managed in order to seek a working problem formulation.

@@

\subsection{Analysis Blocks and Connections}
\label{ss:analysis blocks and connections}
Analysis tools take in a number input variables and then perform some work to calculate 
the values for their respective outputs. In an MDAO graph, this process is 
represented by a group of nodes and edges called an \emph{analysis block}, 
shown in Fig. \ref{f:analysis block}. Within an analysis block each variable 
node represents a single input or output and is connected 
to a single model node via a fixed edge. Note that in Fig.~\ref{f:analysis block}, 
the analysis block contains two model nodes, with a single edge connecting them. 
This edge represents the necessary calculations to map given inputs 
to proper output values. If constructing a weighted graph, the weight calculation edge 
provides the opportunity to computational cost. However, it is also allowed to skip 
this edge and have both incomming and outgoing edges to variables through a single model 
node for a given analysis block. Although analysis blocks are comprised of multiple nodes and edges, since all 
the edges within them are fixed, they become fixed sub-graphs within a graph.

@@

Variable nodes in an analysis block can be distinguished as either an input or 
an output by the manner in which they are connected. As shown in Fig.~\ref{f:analysis block}, 
inputs are any variable nodes that have an outgoing edge into a model 
node. Conversely, outputs are any variable nodes that have an incoming edge from a model node.

@@

So a design variable is defined as any variable node with $\txt{deg}_l^-(v)=0$. 
This, by definition, means that design variables are not holes in the graph, since 
they have not violated their lower indegree limit. Regardless, 
when working with a MCG or FPG, only connection edges are allowed, so a design 
variable in either graph will be a variable with no incomming edges edges. For a valid PSG 
any design variable node would have at least one, but possibly multiple, incomming 
implicit edges from one or more driver nodes.

@@

  Simply stating that any node or block with incomming or outgoing edges
  from more than one other node or block is global works glosses over a more 
  subtle aspect of some MDAO problems. The locality of any node in a graph is 
  a relative property. For instance, a single node might have outgoing edges 
  to two separate analysis blocks, $A$ and $B$, but none to a third, $C$. Then 
  you could say that this node was global with respect to $A$ and $B$, but local 
  to the group $A,B$ with respect to $C$. This situation produces a natural 
  hierarchy in a graph, where you could form increasingly smaller groups as you 
  segment problem into finer localities.

  When solving a problem using a heirarchical decomposition approach, 
  there are various techniques for partitioning that are effective in different 
  scenarios \cite{krishnamachari1997optimal,michelena1997hypergraph,
  sobieszczanski1997,Perez2004,allison2009optimal}. Tosserams et al proposed a 
  language based syntax for describing the partitioning of problems, named $\Psi$
  \cite{tosserams2010specification}. $\Psi$ provides an opposing perspective to 
  this work, where they compose hierarchies from the bottom up, into larger and 
  larger groups. However, $\Psi$ provides a compiler that can produce a standard 
  problem representation of the assembled problem, and a number of example converters
  from that standard representation to application specific formats. It would be 
  possible to provide such a converter to build a graph form the $\Psi$ format.

  [[Could probably build this and include it in appendix]]

@@

  Coupling exists in a design problem when a set of two or more analyses each depend on the
  others outputs. In the Sellar problem from Eqn \ref{eqn:simple_fpf} the two 
  coupling constraints, $G_1$ and $G_2$ provide a reciprical dependence between 
  $D_1$ and $D_2$. In a graph, these constraints show up as connection edges between 
  the outputs of each analysis block. The relevant connection edges are highlighted in 
  Fig. \ref{f:coupling}, where they form a cycle. Cycles in a graph are the characteristic 
  structure that represents coupling.

@@

	It is important to note that the coupling cycles do not contain 
	any driver nodes. Solver, optimizer, or other iterative process is 
	invovled in the coupling definition--though one will be necessary for a valid 
  PSG. Additionally, a coupling cycle has no inherant start or end. It would be
  valid to pick any node in the cycle as a starting point, and proceed around the
  loop untill you get back to your starting point. For the Sellar Problem, picking 
  $D_1$ as the starting point would yeild a problem as given in 
	Eqn.~\ref{eqn:simple}, while picking $D_2$ would yield the problem as givne in 
  Eqn.~\ref{eqn:simple2}.

	Larger problems can contain more complex cycles in their FPG, indicating more 
	complex coupling between analyses. A cycle can contain more than 
	just two analysis blocks. Multiple independent cycles can exist, indicating 
	independent coupling relationships. Cycles can also overlap, where the same analysis 
	blocks are involved in multiple different coupling cycles. All of these situations
	arise naturally as the size of problems grows, and managing this coupling may
	become difficult. In the present work, Sec.~\ref{s:example problem}.\ref{ss:obtaining an FPG} 
  will demonstrate how building an FPG from an MCG provides an opportunity to 
  identify and potentailly reduce the number of cycles in a graph.

  If large amounts of coupling are present it can help convergence 
  rates to look for an effective ordering for the execution of analyses.
  Rogers' DEMAID tool uses a genetic algorithm to find an ordering that minimizes 
  the overall coupling of the system by separating independent cycles in the 
  graph \cite{rogers1996,rogers1996demaid}. Rodgers work focused on the matrix 
  form of the DSM for ordering optimization. Lu and Martins more recent work 
  worked with a weighted form of the DSM and used an iterative clustering approach 
  to perform a similar task to DEMAID \cite{Lu2012}.

  However, when using a graph representation, the ordering problem can be greatly 
  simplified. For any given coupling cycle, a Gauss-Seidel iteration pattern 
  is automatically given simply folowing the cycle around the graph. If only 
  once cycle is present, then the task reduces down to selecting a starting point
  in the cycle. When sub-cycles are present each sub-cycle ordering is also 
  given automatically by following the graph, but now a there is freedom at which 
  level to manage the iteration over the cycles. Ordering of many cycles and 
  sub-cycles is still a challenge, but the total search space is reduced by 
  always following the ordering from the graph from a selected starting node.

\subsection{Multi--fidelity Problems}
	\label{ss:multi-fideliy problems}
	A multi--fidelity problem can be characterized by two or more different analyses 
	each calculating the same data. Mapping this type of multi--fidelity situation 
	onto a graph will yield two analysis blocks, each with their own output 
	variable nodes, having outgoing edges to a single variable in a third analysis 
  block that needs the data as input. Figure \ref{f:collision_example} shows 
  a modified version of the Sellar problem with a new analysis, $D_0$, representing a 
  low fidelity version of $D_1$.

	\begin{figure}
	  \begin{center}
	  %\includegraphics[height=.25\textheight]{}
	  [INSERT GRAPH HERE]
	  \caption{Graph of a notional multi-fidelity problem \label{f:collision_example}}
	  \end{center}
	\end{figure}

@@

\subsection{Fundamental Problem Graph}
	\label{ss:FPG}
	We now define the fundamental problem graph $F=(V_F,E_F)$ as a directed graph meeting the following conditions, which are explained subsequently,
	\begin{enumerate}
	\item[(1)] $\displaystyle{I_F \subset I}$ such that the remaining conditions hold
	\item[(2)] $\displaystyle{ \forall i \in I_F, \ \exists v \in V_{A_i} \txt{ with } t_\txt{node}(E^{-1}(v))=\txt{`model'} \txt{ and } \txt{deg}^+(v)>0 }$
	%\item[(3)] $\displaystyle{ \forall i \in I, \forall v \in V_{A_i} \txt{ with } t_\txt{node}(v) = \txt{`variable,'} \  \txt{deg}_l^-(v) < \txt{deg}^-(v) \leq \txt{deg}_u^-(v)}$
	%\item[(3)] $\displaystyle{ \forall i \in I, \forall v \in V_\txt{out} \txt{ with } t_\txt{node}(v) = \txt{`variable,'} \  \txt{deg}_l^-(v) < \txt{deg}^-(v) \leq \txt{deg}_u^-(v)}$
	\item[(3)] $\displaystyle{V_{\txt{in},F} = \{v \in V_\txt{in} \st \txt{deg}^+(v) > 0\} }$ ((maybe this should be 1 instead of 0 to match the previous definition of global input))
	\item[(4)] $\displaystyle{V_F = V_{\txt{in},F} \cup V_\txt{out} \cup \left( \bigcup_{i \in I_F} V_{A_i} \right)}$
	\item[(5)] $\displaystyle{E_F = C_F \cup \left( \bigcup_{i \in I_F} E_{A_i} \right), \ C_F \subset C_M}$
	\item[(6)] $\displaystyle{\forall v \in V_F \txt{ with } t_\txt{node}(v) = \txt{`variable,'} \  \txt{deg}_l^-(v) \leq \txt{deg}^-(v) \leq \txt{deg}_u^-(v)}$
	\end{enumerate}
	The set $I_F$ is an index set containing the indices of the analysis blocks in $F$ and it may only include the analysis blocks $A_i$ that meet requirements (2) and (6). 
	Requirement (2) stipulates that each analysis blocks in $F$ must have at least one local output that is being used. 
	Requirement (3) stipulates that only the global inputs that are being used should be included. 
	Requirements (4) and (5) provide the construction of the sets of nodes and edges, respectively. 
	Lastly, requirement (6) stipulates that the number of edges directed into the variable nodes must be within the lower and upper indegree limits; if $\txt{deg}^-(v) < \txt{deg}_l^-(v)$ the node is called a \emph{hole}, and if $\txt{deg}^-(v) > \txt{deg}_u^-(v)$ the node is called a \emph{collision}.

@@

	%Then, mathematically, the FPG starts with $\mathcal A_1 = \{1,\ldots,m\}$, $I_{F,1} = I$, and $C_{F,1} = C_M$.
	Then, mathematically, the FPG starts with $C_{F,0} = C_M$, $E_{F,0} = E_M$, $V_{F,0} = V_M$.
	The nodes where $\txt{deg}^-(v) < \txt{deg}_l^-(v)$ are considered first.
	\begin{enumerate}
	\item The first step is to detect holes and disconnect the connection edges following them. These connection edges are removed because they represent variables which cannot be determined because the analysis function does not have adequate inputs. The set of variable nodes which are holes is created as
	\begin{equation}
	H = \{v \in V_M \st t_\txt{node}(v) = \txt{`variable'} \txt{ and } \txt{deg}^-(v) < \txt{deg}_l^-(v) \},
	\end{equation}
	which is the set of variable nodes with fewer incoming edges than are allowed by the lower indegree limit.
	Then the updated set of edges is created by removing the first set of connection edges following the hole:
	\begin{equation}
	C_{F,1} = C_{F,0} \setminus \{(x,y) \in E_M \st x=E_M^3(v) \txt{ for } v \in H\},
	\end{equation}
	%deg-v is now recaculated for the new C. 
	and this step is demonstrated by Fig.~\ref{f:hole}. Because removing these edges can create new holes, this step must be repeated until no more holes are found.
	\begin{figure}[htb!]
		\begin{center}
		\includegraphics[width=3in]{images/analysis_block_hole}
		\end{center}
		\vspace{-20pt}
	\caption{Example variable node indicating a hole.}
	\label{f:hole}
	\end{figure}

	\item The second step is to detect collisions and to then disconnect enough connection edges so that the collisions are resolved. The set of variable nodes which contain collisions is created as
	\begin{equation}
	S_\txt{nodes} = \{v \in V_M \st t_\txt{node}(v) = \txt{`variable'} \txt{ and } \txt{deg}^-(v) > \txt{deg}_u^-(v) \}.
	\end{equation}
	For each collision node we can construct a set contained the edges directed in. The set containing all of these sets is constructed as
	\begin{equation}
	S_\txt{edges} = \big \{ \{(x,y) \in E_M\} \st y \in S_\txt{nodes} \big \}
	\end{equation}
	Let $J=\{1,2,\ldots,|S_\txt{edges}|\}$ be an indexing set for $S_\txt{edges}$ such that each $S_{\txt{edges},j}$ corresponds to a set in $S_\txt{edges}$ for $j \in J$. 
	An example collision is shown in Fig.~\ref{f:collision} to indicate the definition of $S_{\txt{edges},j}$. 
	We can assume that $J$ also indexes $S_\txt{nodes}$ because there is a one--to--one correspondence between the elements in $S_\txt{nodes}$ and the elements in $S_\txt{edges}$ (which are sets). 
	Then we may construct sets of edges as
	\begin{equation}
	B_j = \big \{e_k \in S_{\txt{edges},j} \st k \in \{1,2,\ldots,K\} \txt{ with } K \leq \txt{deg}_u^-(v_j) \big \}, \ j \in J,
	\end{equation}
	which means that each set $B_j$ is constructed from the set $S_{\txt{edges},j}$ by taking only as many edges as are allowed by the upper indegree limit of $v_j$. The construction of each $B_j$ corresponds to making a decision on which edges to include and which edges not to include. Then let
	\begin{equation}
	C_{F,2} = \{ e \in C_{F,1} \st e \in B_j \txt{ for some } j \in J\},
	\end{equation}
	\begin{equation}
	E_{F,2} = E_M \setminus (C_M \setminus C_{F,2})
	\end{equation}
	and
	\begin{equation}
	F_2 = (V_M,E_{F,2})
	\end{equation}
	\begin{figure}[htb!]
		\begin{center}
		\includegraphics[width=3in]{images/analysis_block_collision}
		\end{center}
		\vspace{-20pt}
	\caption{Example variable node indicating a collision.}
	\label{f:collision}
	\end{figure}
